Landau quantization of nearly degenerate bands

### 2018-09-15 paper.tex
Updates from ShareLaTeX

\begin{figure}
\includegraphics[width=0.9\columnwidth]{orbits.png}
\caption{(a) \textbf{[some axes will be helpful]} Solid (resp.\ dashed) lines respectively illustrate the band dispersion of an electron gas with (resp.\ without) Rashba spin-orbit coupling.  The oriented circles illustrate the spin-orit-split orbits for a magnetic field pointing to $-z$ direction. \textbf{[might replace Delta with $2\alpha k_E$ at some point]} (b) The zeroth-order orbit $\frako_0$ is indicated by a dashed circle with area $S$; $\delta S$ is the differential area  between two spin-orbit-split orbits. The spin texture is indicated by purple arrows.\label{fig:orbits}}
\end{figure}

>>>>

\begin{figure}
\includegraphics[width=0.9\columnwidth]{orbits.png}
\caption{(a) Solid (resp.\ dashed) lines respectively illustrate the band dispersion of an electron gas with (resp.\ without) Rashba spin-orbit coupling.  The oriented circles illustrate the spin-orit-split orbits for a magnetic field pointing to $-z$ direction. (b) The zeroth-order orbit $\frako_0$ is indicated by a dashed circle with area $S$; $\delta S$ is the differential area  between two spin-orbit-split orbits. The spin texture is indicated by purple arrows.\label{fig:orbits}}
\end{figure}
